---
title: "R Notebook"
output: html_notebook
---

# Use package `yaml` to modify a YAML field in a post

```{r}
blog_dir = '/media/msfz751/2560x/repos/blogdown-sites/fonzie-oilgains'
file <- file.path(blog_dir, "content/blog", "2018-11-18-otc-2016-second-day.md")
file
```

```{r}
# read markdown file
x <- xfun::read_utf8(file)
res <- blogdown:::split_yaml_body(x)   # split in two
res_yaml <- res$yaml    # character vector
res_yaml
```

```{r}
# read from a character vector and convert to R objects
library(yaml)
res_li <- read_yaml(text = res_yaml)   # read and convert to a list
res_li
```

```{r}
# change a value in a YAML field
res_li$image <- "featured.jpg"
res_li
```

```{r}
con <- file("data-res.yml", "w")
write_yaml(res_li, con)
```

```{r}
class(res_li)
print(res_li$image)
```

```{r}
yaml.load_file("data-res.yml")
```

# write special YAML

```{r}
link_text <- "
links:
- icon: linkedin
  icon_pack: fas
  name: LinkedIn
  url: ''
"
link_text
```


```{r}
library(yaml)
yaml.load(link_text)
```

```{r}
two_links_txt <- "links:\n - icon: flask\n  icon_pack: fas\n  name: demo slides\n url: ../../slides/rladies-demo-slides.html \n - icon: github\n  icon_pack: fab\n name: demo code\n  url: https://github.com/rbind/apreshill/blob/master/static/slides/rladies-demo-slides.Rmd" 

links_yaml <- as.yaml(two_links_txt)
links_yaml
cat(as.yaml(two_links_txt))
```

```{r}
two_links_txt <- "links:\nicon: flask\nicon_pack: fas\nname: demo slides"
yaml.load(two_links_txt)
```


```{r}
write_yaml(yaml.load(two_links_txt), file = "links.yaml")
```


```{r}
links <- list()
links <- link_one <- list(
    links$icon <- "the icon",
    links$icon_pack <- "fas",
    links$name <- "demo slides"
)
```

        - the icon
        - fas
        - demo slides

```{r}
links <- list(link_one, link_two = list(
    icon = "the icon",
    icon_pack = "fas",
    name = "demo slides"
))
```

    '':
    - the icon
    - fas
    - demo slides
    link_two:
      icon: the icon
      icon_pack: fas
      name: demo slides


```{r}
write_yaml(links, file = "links.yaml")
```


```{r}
yaml.load("foo: 123\nbar: 456")
```

```{r}
links <- list(links = 
    list(icon = "flask", name = "demo"),
    list(icon = "git", name = "github")
)
```

    links:
      icon: flask
      name: demo
    '':
      icon: git
      name: github

# Writing a nested list of links

```{r}
alist <- list(links = list(
    list(icon = 'flask', icon_pack = 'fas', name = 'demo slides', url = ''), 
    list(icon = 'github', icon_pack = 'fab', name = 'demo code', url = '')
    ))
alist
```

    links:
    - icon: flask
      icon_pack: fas
      name: demo slides
      url: ''
    - icon: github
      icon_pack: fab
      name: demo code
      url: ''


```{r}
write_yaml(alist, file = "links.yaml")
```


links:
- icon: flask
  icon_pack: fas
  name: demo slides
  url: ../../slides/rladies-demo-slides.html
- icon: github
  icon_pack: fab
  name: demo code
  url: https://github.com/rbind/apreshill/blob/master/static/slides/rladies-demo-slides.Rmd
